Global Deaths Due to Air Pollution

### 2022-05-03 outline.Rmd
nothing to see here

percent_high<- affected_high %>% ggplot(aes(x = year, y = percent_high, color = country))+
  geom_point() +
  labs(title = "High Population Countries Affected by Air Pollution") +
  xlab("Year")+
  ylab("Percent (total_deaths/average pop)")
ggplotly(percent_high)

>>>>

percent_high<- affected_high %>% ggplot(aes(x = year, y = percent_high, color = country))+
  geom_line() +
  labs(title = "High Population Countries Affected by Air Pollution") +
  xlab("Year")+
  ylab("Percent (total_deaths/average pop)")
ggplotly(percent_high)
